Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-19 docs/manuscript/manuscript.tex
Last paragraph for Cluster Methodology section.

\subsection*{Cluster analysis}
% 1. Clustering focusing on 11 water accessibility variables
% 2. Different clustering algorithm for initial analysis
% 3. Determination and analysis of best cut and hierarchical clustering method
% 4. Election of the best clustering
% 5. Analysis of Ward.d2 & 4 cut tree analysis

We elected 11 variables that describe water accessibility of 78 countries around the world \citep{price2019difference}. Next, we decided to implement clustering which is an unsupervised machine learning method to identify and group water accessibility variables in large data set to understand and make inferences about particular water accessibility variables. All of the clustering analysis was assisted by using the R program. Clustering ultimately can continue to assist in discovering the water accessibility predictor variables.

@@

>>>>

\subsection*{Cluster analysis}
We elected 11 variables that describe water accessibility of 78 countries around the world \citep{price2019difference}. Next, we decided to implement clustering which is an unsupervised machine learning method to identify and group water accessibility variables in large data set to understand and make inferences about particular water accessibility variables. All of the clustering analysis was assisted by using the R program. Clustering ultimately can continue to assist in discovering the water accessibility predictor variables.

@@

Lastly, we developed a horizontal dendrogram using R focusing on Ward.D2 methodology for clustering. We also cut the dendrogram in 4 trees as an 'NBClust' analysis. The clustering trees can be further be analyzed and the results and analysis will be discussed in the results and discussion section.
